---
name: Analisa
surname: Coppens
position: "Student"
pronouns: she/her
address: "3409 Keller Street"
phone: (209) 404-9650
email: "analisa.nicole25@gmail.com"
github: acoppens25
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Skills

I am proficient in technical tools such as GitHub, MEGA, RStudio, and Microsoft Office. My lab and research experience includes PCR, gel electrophoresis, sterile techniques, DNA extraction, and data collection and analysis. I also have strong communication skills and enjoy collaborating in group settings and peer-based projects. 

# Work Experience

```{r}
tribble(
  ~ Title, ~ Dates, ~ Company, ~ Where, ~ Details,
  "Courtesy Clerk", "2019-2020", "Safeway", "Modesto, CA", 
    list("Assisted customers, maintained cleanliness, and provided general support."),
  "General Merchandise Expert", "2020–Present", "Target", "Riverbank, CA", 
    list("Organized merchandise and ensured shelves were accurately labeled and well-stocked.")
) %>%
  detailed_entries(Title, Dates, Company, Where, Details)
```
# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "High School Diploma", "2019", "Beyer High School", "Modesto, California",
   "Biology Transfer","2022", "Modesto Junior College", "Modesto, California",
  "BS Biological Science, Conc. Organism, Ecology, and Evolution", "2022–2026", "CSU Stanislaus", "Turlock, CA") %>%
  detailed_entries(Degree, Year, Institution, Where)
```


# Awards

```{r}
tribble(
  ~ AwardName, ~ Dates,
  "National Honor Society", "2022"
) %>%
  detailed_entries(AwardName, Dates)
```
